---
title: "`QA_That` platform for testing out (QA) tables "
output: html_notebook
author: George Papadopoulos
---


## Intro 


The obvious inspiration comes from the `test_that` package in R that in turn was inspirted from test practices applied in C#, Java, Python etc. Many thanks to all the developers.

**Things may change as development progresses so do keep in mind that.**


The concept here is to include `tests` that are combined into a `checks` that are in turn collected into `sesctions` for each area/code we want to QA.


More specifically, the collection here wil aim at including the following:

+ The basic element, the atom of QA will be the `test`:
    + `test_equal`
    + `test_identical`
    + `test_match`
    + `test_numeric`
    + `test_character`
    + `test_true`
    + `test_false`
    + `test_NA`
    + any other that may arise in the future
+ The `tests` will be combined into `checks` as follows:
    + `check_that("text description", {test_equal(...), test_identical(...). ...}  )`
    + output will be a sumam ry of the whole process
    + see if warnings can be caught there as well
    + Other items to be added in the future
+ Tests will be combined into `QA_that_` sections regarding spcecific areas  i want to QA
    + `QA_that_`(s) are files containing all checks that need to be conducted in the project. The corresponding filenames will need to start with
    `QA_that_` so as to distinguish them from anything else and also they need to be included in a `QA_that` folder
    + `QA_that_`(s) can be fore example tests that need to be conducted in A or B tables in PRSQ
    + For better structure all files should start with `QA_that_` prefix so as to be able to collect results better


More to be aded as we go along with coding 



```{r}

library(tidyverse)
library(emojifont)
library(purrr)
library(magrittr)
library(crayon)
library(QA.that)
# emoji(search_emoji('smile'))



```


## Creating core funcitons

Need also to add code to catch and catalog warnings - to look into that later


```{r}


# test equal function allowing for rounding off if needed


test_equal = function(descr, source_value, test_value, rounding_digits=1, ...){
    
    output = NULL
    
    if(is.numeric(source_value) & is.numeric(test_value)){
    
    
            
            r_sval = round(source_value, digits = rounding_digits)
            r_tval = round(test_value, digits = rounding_digits)
            
            
            if(r_sval == r_tval){ output = T}
            else if(r_sval != r_tval){ output = F}
            
            
            
            
            
    }else {stop("Values must be numeric. To test for text values use test_match() instead.")}
    
   
    # assign global variables to keep track between different checks etc
    assign("global_output", add_row(.GlobalEnv$global_output, test_description = descr, outcome = output), envir = .GlobalEnv )
    
    # browser()    
    # return(output)
    
    
}



test_identical = function(descr, source_value, test_value, ...){
    
    output = NULL
    
    if(is.numeric(source_value) & is.numeric(test_value)){
            
            if(source_value == test_value){ output = T}
            else if(source_value != test_value){ output = F}
            
    }else {stop("Values must be numeric. To test for text values use test_match() instead.")}
    
    
    
    # assign global variables to keep track between different checks etc
    assign("global_output", add_row(.GlobalEnv$global_output, test_description = descr, outcome = output), envir = .GlobalEnv )
    
    # return(output)
    
}




test_match = function(descr,source_value, test_value, ...){
    
    output = NULL
    
    if(is.character(source_value) & is.character(test_value)){
            
            if(source_value == test_value){ output = T}
            else if(source_value != test_value){ output = F}
            
    }else {stop("Values must be characters. To test for numeric values use test_equal() or test_identical() instead.")}
    
    # assign global variables to keep track between different checks etc
    assign("global_output", add_row(.GlobalEnv$global_output, test_description = descr, outcome = output), envir = .GlobalEnv )
    # return(output)
    
}





```




## Adding `tests` to a `check`


start here:

+ check that the function outputs the arguments correctly and continue with the rest of the `test` functions implementation - test OK
+ introduce `tryCatch` segments to the `check_that` structure - **to be created**
+ some changes made to the check that function and the code now works as intended. The code segment evalueates properly and the global variable(s) are updated as expected. 
+ the items to complete now includeadding further functionality to the `check_that` function and make it informative enough to the user by including textual aids in the form of a text ouput progress report in the console. - Initial pass OK



+ The idea now is to create a global storage varioable at a "QA_that" level so as to probvide overall checks for each QA file - remember the QA strucure will need to include the following

    + `QA_that_***` file that will contain all the checks
    + Multiple (possible) `check_that` segments that will contain tests
    + Multiple `test_that` segments that will contain the idividual tests

+ will now need to a way to summarise the overall process so a global variable at `QA_that` level will be required - **completed**
+ in addition, a constructor function to add all components needed before the QA process starts (?), for example: **completed**
    
    + Add or initialise global containers where this is not possible in the amin tests
    + create directories for the QA process
    + more to be added later (?)







```{r}

# global_output = tibble(test_description = character(), outcome = character())



check_that = function(check_desc,code, ...){
    
    # initialise global container variable
    global_output = tibble(test_description = character(), outcome = logical())
    
    # assign and create a global version of the variable
    assign("global_output", global_output, envir = .GlobalEnv)
    
    #evaluate the tests
    eval(code)
    
    #save to global envir and updawte with the check description
    .GlobalEnv$global_output %<>% add_column(check_description = check_desc, .before = "test_description")
    
    
    # housekeeping and presentation
    
    if(sum(.GlobalEnv$global_output$outcome) == dim(.GlobalEnv$global_output)[1]){
        cat(paste0("\n Checking that: ", check_desc, " .... PASS ", sample(emoji(search_emoji('smile')), 1, replace = T )))
    }else{
        not_pass = .GlobalEnv$global_output %>% filter(outcome == F)
        cat(paste0("Checking that: ", check_desc, " ... FAIL \u274c ", "\n"))

    }

    
    cat("\n Summary of checks:-------------------------------------", "\n")
    cat(paste0(.GlobalEnv$global_output$test_description, " \t ---->",if_else(.GlobalEnv$global_output$outcome, paste0("\t PASS ", green("\u2714"),"\n"), 
                                                                              "\t FAIL \u274c \n") ) )
    cat("-------------------------------------------------------")
    
    
    
    
    ## create another global storage in a "QA_that" level so as to store overall QA level results 
    
    # 
    # # to bind to a globeal oveall variable combining all checks in a file
    # assign("global_overall_output", rbind(.GlobalEnv$global_overall_output, .GlobalEnv$global_output), envir = .GlobalEnv)
    # 
    
    return(.GlobalEnv$global_output)
    
    
}





output1 = check_that(check_desc = "numeric is matching", {test_equal(descr = "test description text", 11,11)
                                                    test_equal(descr = "test description text", 12,12)
                                                    test_identical(descr = "test description text", 12,12.1)})


output2 = check_that(check_desc = "text is matching", {test_match(descr = "test description match text", "DFD","DFD")})


# ✗ = \u2717  BALLOT X
# ✘ = \u2718  HEAVY BALLOT X
# ❌ = \u274c CROSS MARK
# × = \u00D7  MULTIPLICATION SIGN
# ╳ = \u2573  BOX DRAWINGS LIGHT DIAGONAL CROSS
# ☓ = \u2613  SALTIRE (St. Andrew's Cross)
# ✕ = \u2715  MULTIPLICATION X
# ✖ = \u2716  HEAVY MULTIPLICATION X
# ⨉ = \u2A09  N-ARY TIMES OPERATOR
# ✓ = \u2713  CHECK MARK
# ✔ = \u2714  HEAVY CHECK MARK
# 







```




## Adding `use_QA` function to create QA structure

**Completed**

Thisngs tro remember are as follows:

+ QA files should start with `QA_that_` so that they make sense and also to enbable the system to pick them up esier. For examnple `QA_that_A_tables_are_in_line_with_B.R`
+ a number of global variables are crated to keep track of things. You wont need to worry about that when coding tests - Discontinued
+ all QA should be in one folder and the starting point is considered the root directory of your project
+ IMPORTANT: the function `use_QA()` needs to be run from your console  in the root directory - otherwise the folders will be created in the folder where the function resides!
+ to add more as needed




```{r}

QAname = "Atables_etc" # to test function

use_QA = function(QAname){
    
    # browser()
    root = getwd()
    QA_folder_path = paste0(root, "/QA_that")
    QA_file_w_path = paste0(QA_folder_path,"/","QA_that_",QAname,".R")
    QA_file_name = paste0("QA_that_",QAname,".R")
    
    log_dir = paste0(root,"/QA_that/QA_logs") # log files directory

    
    ## create a QA folder to house the tests etc
    
    if(dir.exists(QA_folder_path)){
        stop(paste0("directory ", "`QA_that`", " alrady exists. Consider renaming it to keep existing tests.
             Ideally one such QA folder should exist per project to avoid confusion."))
    }else{
        
        dir.create(QA_folder_path)
        cat(paste0("\n", "directory ","`QA_that`", " was created ----> ", green("\u2714")))
        
    }
    
    ## to write the first file
    
    if(file.exists(QA_file_w_path)){
        stop("file exists in destination directory. Consider renaming.")
    }else{
        file.create(QA_file_w_path)
        cat(paste0("\n", "file ",QA_file_name, " was created ----> ", green("\u2714")))
        
    }
    
    
    
    ## adding global container variable to collect results from all `check_that`sections - Disontinued as it would be better to have each QA stream separate
    ## and collect results in each
    
    # global_check_that = tibble(check_description = character(), test_description = character(), outcome = logical())
    
    
    # to get the path of the current file if needed
    # full_script_path = rstudioapi::getSourceEditorContext()$path

    # current_script = str_extract(full_script_path, "QA_that_.+\\.R$")

    # create folder to save the log file (s)
    
    
    if(dir.exists(log_dir)){
        stop("QA logs directoryexists. Consider renaming.")
    }else{
        dir.create( log_dir )
        cat(paste0("\n", "QA_logs directory was created ----> ", green("\u2714")))
        
    }
    
    
    
    
    
}


use_QA("tables A match B")



```




## adding `summary` function

will need  to add an option to delete and reuse the same file in case multiple runs are needed.


```{r}




map_write_to_log = function(check_d, log_df, log_file){
    
    # browser()

    
    # check_d = log_df$check_description
    test_d = log_df$test_description
    test_outcome = log_df$outcome %>% if_else("\u2714", "\u274c") # tick or else a cross
    
    

    
    
    cat(paste0("\n Checking that: ", check_d[1], " ############################### \n \n"), file = log_file)
               
    cat(paste0("\t \t", test_d," ----------> ", test_outcome), file = log_file, sep = "\n" )
    
    
    if(!is.character(check_d)){
        cat( "\t  Check Description is not a character string... Make sure the log data frame is structured properly \n", file = log_file, sep = "\n" )
    } else if(is.null(check_d)){
        cat("\t  The check descriptiopn is null (empty) \n", file = log_file, sep = "\n" )
    } else if(is.null(log_df)){
        cat("\t  The log data frame is null (empty) \n")
    }else {
        
        cat("\t -------------------------------------------------------------", file = log_file, sep = "\n")
        cat("\t  log data frame and check descriptions look OK", file = log_file, sep = "\n"  )
        cat("\t -------------------------------------------------------------", file = log_file, sep = "\n")
        
        }
    
    
    
    # Check Description has multiple entries for a single group
    
    return(TRUE)
    
    
}





map_write_to_log(output1)



cat(paste0("\n Checking that: ", check_desc, " .... PASS ", sample(emoji(search_emoji('smile')), 1, replace = T )))

rstudioapi::getSourceEditorContext()$path




summary_QA = function(..., log_file_name = NULL, del.flag = T){
    
    # browser()
    
    dots = list(...)
    
    log_df = map_dfr(dots, rbind)
    
    # get the file name of the current script
    # create a directory for the logs
    
    
    root = getwd() # get root
    log_dir = paste0(root,"/QA_that/QA_logs") # log files directory
    log_fname_w_path = paste0(log_dir,"/", log_file_name)

    
    if(is.null(log_file_name)){
        stop("log file name is NULL. Consider naming the log file to be created.")
    }else if(del.flag){
        unlink(log_fname_w_path)
        cat("Deleting file from previous run --> del.flag==T")
    }
    
    
        
    log_file = file(log_fname_w_path, open = "a") #open a  file and have it ready to append text to it

    
    ### to get the file name just right here -  it has .r at the end
    # browser()
    
    if(!dir.exists(log_dir)){
        dir.create(paste0(root,"/QA_that/QA_logs"))
        cat(paste("creating QA_logs directory in `QA_that` folder"))
    }
    
    
    
    # group the log data frame 
    log_df_grouped = log_df %>% group_by(check_description) %>% nest()
    
    
    # now use a map to paste to the log file for each category
    
    map2( log_df_grouped$check_description, log_df_grouped$data, map_write_to_log, log_file = log_file)
    
    
    ## START HERE
    
    
    return(log_df)    
    

    
}




aa = summary_QA(output1,output2, log_file_name = "log1.txt", del.flag = T)





```




### To test functions etc

```{r}

sourceVal = 121.1234
testVal = 121.1333

test_equal(source_value = sourceVal, test_value = testVal, 2)


sourceVal = 121
testVal = "121"

test_identical(source_value = sourceVal, test_value = testVal)



sourceVal = "121"
testVal = "121"

test_match(source_value = sourceVal, test_value = testVal)


eval(5+5)


eval({1+5})


check_that("1212!", {5+3})

aa = check_that("1212!", {aa.1 = test_identical(1,1)
                    aa.2 = test_equal(11.12,12)}, b = 1)

ab  = as.list(environment(check_that("1212!", {test_identical(1,1)}) ))


(2+3)
a = {2+3; 4+5}
(invisible(2+3))
{invisible(2+3)}


############# test dynamically augmented check list

check_that(check_desc = "a check description here", {test_equal(descr = "a description here", 11.1,12)})




test_equal(descr = "a description here", 11.1,12,check_desc = "general check")

test_match(descr = "test for a match", "2323", "2323")

test_identical(descr = "test for identical numerical match", 2323, 2323)

test_identical(descr = "will it pass now?", 2323.1, 2323)


global_output




```



## conduct QA tests


```{r}


## run the following function first - THIS NEEDS TO RUN FROM THE ROOT DIRECTORY ELSE IT WILL CREATE THE FOLDER IN THE DIRECTORY WHERE THE RM FILE RESIDES !!!
## 
## 
## 
use_QA(QAname = "QA_filename")


output44 = check_that(check_desc = "numeric matching test 1", {test_equal(descr = "test description text", 11,11)
  test_equal(descr = "testing vectorization",c(1,2,2,3),c(1,2,3,5))
  test_identical(descr = "test description text", 12,12.1)
  test_match(descr = "checking that two test strings match", "DFDF","dfdf")})


output33 = check_that(check_desc = "text round 2", {test_match(descr = "test description match text", "DFD","DFD")})



output45 = check_that(check_desc = "test round 3", {test_equal(descr = "test rounding equal 11 with 11.3 ", 11,11.3, rounding_digits = 0)
  test_equal(descr = "check that 12 matches with 12.2 using rounding up", 12,12.4, rounding_digits = 0)
  test_identical(descr = "test description text", 12,12.1)
  test_identical(descr = "check identical  that 10 i s equal to 10.2 ", 10,10.1)
  test_match(descr = "checking that two test strings match", "DFDF","dfdf")
  
  
  
})




bb = summary_QA(output44,output33, output45, log_file_name = "log_that_other_file.txt")



test_equal(descr = "erere",source_value = c(1,2,3),test_value = c(1,2,5))


```























